NGO Repression as a Predictor of Worsening Human Rights Abuses

### 2021-11-17 manuscript/manuscript.Rmd
Minor typos

Law 84 (and its replacement Law 70 of 2017) is thus a useful lever for selectively controlling the allowable space for dissidence and leaving open the possibility of future human rights abuses. The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously provides the government the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.

This trend holds across many other countries as well. For instance, even though India passed an anti-NGO law (containing multiple bariers to funding and advocacy) in 1976, it has not always been uniformly implemented. Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [@Chaudhry:2022]. Anti-NGO laws can therefore serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law, explaining why de facto levels of NGO repression serve as a stronger predictor of worsening respect for human rights abuses.

>>>>

Law 84 (and its replacement Law 70 of 2017) is thus a useful lever for selectively controlling the allowable space for dissidence and leaving open the possibility of future human rights abuses. The law's built-in discretionary authority permits the government to give the appearance of concessions and openness to civil society while simultaneously providing the government with the ability to target individual NGOs and reserving the right to engage in broader crackdowns of associational rights.

This trend holds across many other countries as well. For instance, even though India passed an anti-NGO law (containing multiple barriers to funding and advocacy) in 1976, it has not always been uniformly implemented. Rather, having an anti-NGO law on the books serves the state's long-term strategic interests, enabling it to crack down on NGOs when they start posing electoral or economic threats to the state [@Chaudhry:2022]. Anti-NGO laws can therefore serve as a useful avenue for future human rights abuses, sometimes with years separating the official passage of the law and the large-scale implementation of the law, explaining why de facto levels of NGO repression serve as a stronger predictor of worsening respect for human rights abuses.
